### 2014-09-06 abstract.tex
minor

\begin{abstract}
Predictive analysis has recently emerged as a promising technique for 
sound detection of multithreading bugs (i.e., without false alarms). 
The idea is to start from an instrumented execution trace, and transform 
it based on the concrete information it provides, such as concrete values 
and memory accesses, to expose bugs, while preserving feasibility. For
example, the analysis may reorder trace events to simulate different thread schedules, 
as long as value flow dependencies are preserved.

>>>>

\begin{abstract}
Predictive analysis has recently emerged as a promising technique for 
sound detection of concurrency bugs (i.e., without false alarms). 
The idea is to start from an instrumented execution trace, and transform 
it based on the concrete information it provides, such as concrete values 
and memory accesses, to expose bugs, while preserving feasibility. For
example, the analysis may reorder trace events to simulate different thread schedules, 
as long as value flow dependencies are preserved.

### 2014-09-06 eval.tex
submitted version
minor

{\bf Evaluation Method} We conducted our experiments on a set of 16 
applications, which were also used to evaluate {\sf RV}. Specifically, 
the set includes large applications such as {\sf Jigsaw}, 
{\sf Xalan} and {\sf Lusearch}. To handle large applications that make 
use of reflection, we applied the {\sf Tamiflex} tool~\cite{tamiflex}, which 
replaces reflective calls with the concrete method invocations recorded 
in the observed run.
% for the purpose of effective static analysis.  
We omit the benchmark {\sf eclipse} because the current version 
of {\sf Tamiflex}  leads to abnormal execution after the instrumentation, 
which throws an exception when the main service is started. 
By applying \tool\  to the abnormal execution, we identify only 3 races, 
similarly to the report of RV~\cite{pldi14}.
In addition, the {\sf montecarlo} benchmark requires an external input 
that we downloaded from the internet and simplified. For the large 
applications, we utilized the most lightweight available configuration.
To further control the cost of our experiments, we monitored each execution for at most 10 minutes.

As the detection capability  depends on the observed run, for fair 
comparison we monitor the execution once by recording all necessary 
information required by both approaches, and then apply both techniques 
to the monitored run. Besides, our reported data for RV may be different 
from the original report for two reasons: (1) the different observed runs 
lead to different sets of races, (2) the original implementation of RV 
contains a bug in branch identification, which leads to  misses of 
many branches and  incorrect reduction of dependences during the analysis. 
We confirmed the bug with the author and fixed the bug in our 
experiments.\footnote{We have created an in-depth report on the bug, 
along with a witness test case. (See:  \url{https://sites.google.com/site/recipe3141/}.)}

@@

\begin{table*}[htbp]
\caption{Relaxed Analysis}
\begin{tabular}{|l|r|r|r|r|l|r|r|r|r|r|r|r|r|r|}
\hline
 & \multicolumn{ 7}{c|}{Trace} & \multicolumn{ 3}{c|}{Races} & \multicolumn{ 2}{c|}{Difference} & \multicolumn{ 2}{c|}{Running time (sec)} \\ \hline
Benchmarks & \multicolumn{1}{l|}{Th} & \multicolumn{1}{l|}{Reads} & \multicolumn{1}{l|}{Writes} & \multicolumn{1}{l|}{Base} & Br & \multicolumn{1}{l|}{sync} & \multicolumn{1}{l|}{Total} & \multicolumn{1}{l|}{RV} & \multicolumn{1}{l|}{Recipe-s} & \multicolumn{1}{l|}{Recipe} & \multicolumn{1}{l|}{Diff} & \multicolumn{1}{l|}{Diff'} & \multicolumn{1}{l|}{Recipe} & \multicolumn{1}{l|}{RV} \\ \hline
critical & 3 & 13 & 7 & 5 & 2/13 & 6 & 78 & 8 & 8 & 8 & 0 & 0 & 8 & 2 \\ \hline
airline & 11 & 45 & 15 & 4 & 32/82 & 30 & 317 & 9 & 9 & 9 & 0 & 0 & 490 & 4 \\ \hline
account & 3 & 46 & 21 & 10 & 3/47 & 6 & 227 & 5 & 2 & 5 & 3 & 3 & 41 & 4 \\ \hline
pingpong & 4 & 7 & 7 & 3 & 0/15 & 6 & 111 & 1 & 1 & 1 & 0 & 0 & 19 & 1 \\ \hline
bbuffer & 4 & 640 & 118 & 10 & 634/1.1K & 217 & 3.3K & 9 & 13 & 25 & 21 & 5 & 62 & 5 \\ \hline
bubblesort & 26 & 1.3k & 966 & 121 & 155/2.8K & 322 & 8.4K & 7 & 7 & 7 & 0 & 0 & 3295 & 3 \\ \hline
bufwriter & 5 & 165 & 52 & 75 & 16/130 & 44 & 525 & 2 & 4 & 10 & 8 & 0 & 63 & 9 \\ \hline
mergesort & 5 & 38 & 33 & 5 & 15/472 & 28 & 1.7K & 3 & 3 & 10 & 7 & 0 & 37 & 5 \\ \hline
raytracer & 2 & 31 & 5 & 12 & 314/8,2K & 676 & 94.5K & 4 & 4 & 6 & 2 & 0 & 47 & 2 \\ \hline
montecarlo & 2 & 5 & 86 & 2 & 1.9K/38.2K & 21.1K & 1.9M & 1 & 1 & 4 & 3 & 0 & 1 & 17 \\ \hline
moldyn & 2 & 605 & 61 & 104 & 19.6K/52.6K & 62 & 203.4K & 2 & 6 & 14 & 12 & 0 & 2842 & 1 \\ \hline
ftpserver & 28 & 684 & 299 & 71 & 4.4K/233.3K & 78.2K & 3.9M & 57 & 99 & 152 & 108 & 13 & 811 & 153 \\ \hline
jigsaw & 12 & 525 & 702 & 211 & 63.2K/467.9K & 86.7K & 5.5M & 8 & 17 & 23 & 15 & 0 & 33 & 7 \\ \hline
sunflow & 9 & 2.1K & 1.3K & 473 & 201.3K/827.0K & 50K & 7.1M & 20 & 38 & 78 & 69 & 11 & 4520 & 22 \\ \hline
xalan & 9 & 1.4K & 0.9K & 209 & 15.7K/103.2K & 190.1K & 6.6M & 2 & 2 & 6 & 4 & 0 & 5317 & 10 \\ \hline
lusearch & 10 & 2.3K & 0.5K & 715 & 22.2K/164K & 93.2K & 9.1M & 14 & 27 & 49 & 38 & 3 & 5430 & 8 \\ \hline
\end{tabular}
\label{tab:main}
\end{table*}

@@

\begin{figure}[htp]
\centering
\includegraphics[scale=0.45]{figs/Visio-bbuffer.pdf}
\caption{Relaxation of Inter-thread dependence}\label{fig:relax1}
\end{figure}

@@

\begin{figure}[htp]
\centering
\includegraphics[scale=0.45]{figs/Visio-msort.pdf}
\caption{Relaxation of Paths}\label{fig:relax2}
\end{figure}

>>>>

{\bf Evaluation Method} We conducted our experiments on a set of 16 
applications, which were also used to evaluate {\sf RV}. Specifically, 
the set includes large applications such as {\sf Jigsaw}, 
{\sf Xalan} and {\sf Lusearch}. To handle large applications that make 
use of reflection, we applied the {\sf Tamiflex} tool~\cite{tamiflex}, which 
replaces reflective calls with the concrete method invocations recorded 
in the observed run.
% for the purpose of effective static analysis.  
We omit the benchmark {\sf eclipse} because the current version 
of {\sf Tamiflex}  leads to abnormal execution after the instrumentation, 
which throws an exception when the main service is started. 
By applying \tool\  to the abnormal execution, we identify only 3 races, 
similarly to the report of RV~\cite{pldi14}.
In addition, the {\sf montecarlo} benchmark requires an external input 
that we downloaded from the internet and simplified. For the large 
applications, we utilized the most lightweight available configuration.

As the detection capability  depends on the observed run, for fair 
comparison we monitor the execution once (for a period of 10 minutes) by recording all necessary 
information required by both approaches, and then apply both techniques 
to the monitored run. Besides, our reported data for RV may be different 
from the original report for two reasons: (1) the different observed runs 
lead to different sets of races, (2) the original implementation of RV 
contains a bug in branch identification, which leads to  misses of 
many branches and  incorrect reduction of dependences during the analysis. 
We confirmed the bug with the author and fixed the bug in our 
experiments.\footnote{We have created an in-depth report on the bug, 
along with a witness test case. (See:  \url{https://sites.google.com/site/recipe3141/}.)}

@@

\begin{table*}[htbp]
\caption{Relaxed Analysis}
\begin{tabular}{|l|r|r|r|r|l|r|r|r|r|r|r|r|r|r|}
\hline
 & \multicolumn{ 7}{c|}{Trace} & \multicolumn{ 3}{c|}{Races} & \multicolumn{ 2}{c|}{Difference} & \multicolumn{ 2}{c|}{Running time (sec)} \\ \hline
Benchmarks & \multicolumn{1}{l|}{Th} & \multicolumn{1}{l|}{Reads} & \multicolumn{1}{l|}{Writes} & \multicolumn{1}{l|}{Base} & Br & \multicolumn{1}{l|}{sync} & \multicolumn{1}{l|}{Total} & \multicolumn{1}{l|}{RV} & \multicolumn{1}{l|}{Recipe-s} & \multicolumn{1}{l|}{Recipe} & \multicolumn{1}{l|}{Diff} & \multicolumn{1}{l|}{Diff'} & \multicolumn{1}{l|}{Recipe} & \multicolumn{1}{l|}{RV} \\ \hline
critical & 3 & 13 & 7 & 5 & 2/13 & 6 & 78 & 8 & 8 & 8 & 0 & 0 & 8 & 2 \\ \hline
airline & 11 & 45 & 15 & 4 & 32/82 & 30 & 317 & 9 & 9 & 9 & 0 & 0 & 490 & 4 \\ \hline
account & 3 & 46 & 21 & 10 & 3/47 & 6 & 227 & 5 & 2 & 5 & 3 & 3 & 41 & 4 \\ \hline
pingpong & 4 & 7 & 7 & 3 & 0/15 & 6 & 111 & 1 & 1 & 1 & 0 & 0 & 19 & 1 \\ \hline
bbuffer & 4 & 640 & 118 & 10 & 634/1.1K & 217 & 3.3K & 9 & 13 & 25 & 21 & 5 & 62 & 5 \\ \hline
bubblesort & 26 & 1.3k & 966 & 121 & 155/2.8K & 322 & 8.4K & 7 & 7 & 7 & 0 & 0 & 3295 & 3 \\ \hline
bufwriter & 5 & 165 & 52 & 75 & 16/130 & 44 & 525 & 2 & 4 & 10 & 8 & 0 & 63 & 9 \\ \hline
mergesort & 5 & 38 & 33 & 5 & 15/472 & 28 & 1.7K & 3 & 3 & 10 & 7 & 0 & 37 & 5 \\ \hline
raytracer & 2 & 31 & 5 & 12 & 314/8,2K & 676 & 94.5K & 4 & 4 & 6 & 2 & 0 & 47 & 2 \\ \hline
montecarlo & 2 & 5 & 86 & 2 & 1.9K/38.2K & 21.1K & 1.9M & 1 & 1 & 4 & 3 & 0 & 1 & 17 \\ \hline
moldyn & 2 & 605 & 61 & 104 & 19.6K/52.6K & 62 & 203.4K & 2 & 6 & 14 & 12 & 0 & 2842 & 1 \\ \hline
ftpserver & 28 & 684 & 299 & 71 & 4.4K/233.3K & 78.2K & 3.9M & 57 & 99 & 152 & 108 & 13 & 811 & 153 \\ \hline
jigsaw & 12 & 525 & 702 & 211 & 63.2K/467.9K & 86.7K & 5.5M & 8 & 17 & 23 & 15 & 0 & 33 & 7 \\ \hline
sunflow & 9 & 2.1K & 1.3K & 473 & 201.3K/827.0K & 50K & 7.1M & 20 & 38 & 78 & 69 & 11 & 4520 & 22 \\ \hline
xalan & 9 & 1.4K & 0.9K & 209 & 15.7K/103.2K & 190.1K & 6.6M & 2 & 2 & 6 & 4 & 0 & 5317 & 10 \\ \hline
lusearch & 10 & 2.3K & 0.5K & 715 & 22.2K/164K & 93.2K & 9.1M & 14 & 27 & 49 & 38 & 3 & 5430 & 8 \\ \hline
\end{tabular}
\label{tab:main}
\vspace{-2em}
\end{table*}

@@

\begin{figure}[htp]
\centering
\includegraphics[scale=0.45]{figs/Visio-bbuffer.pdf}
\caption{Relaxation of Inter-thread dependence}\label{fig:relax1}
\vspace{-1em}
\end{figure}

@@

\begin{figure}[htp]
\centering
\includegraphics[scale=0.45]{figs/Visio-msort.pdf}
\caption{Relaxation of Paths}\label{fig:relax2}
\vspace{-2em}
\end{figure}
